Automated Synthesis of State-Space Digital Systems

### 2016-12-20 cav2017/cav2017.tex
typos + line breaks in introduction

Linear Time Invariant Control systems represnt a sizeable portion of modern
embedded software, performing highly non-trivial control
tasks, with significant impact in numerous application areas such as
environmental control, navigation and robotics~\cite{astrom1997computer,Franklin15}.

@@

In this paper, we propose the synthesis of control algorithms for cyberphisical
systems taking into consideration the continuous domain of the plant alongside
the discrete domain of the controller and the hybrid elements that communicate
them.

>>>>

Linear Time Invariant Control systems represent a sizeable portion of
modern embedded software, performing highly non-trivial control tasks,
with significant impact in numerous application areas such as
environmental control, navigation and
robotics~\cite{astrom1997computer,Franklin15}.

@@

In this paper, we propose the synthesis of control algorithms for
cyberphysical systems taking into consideration the continuous domain
of the plant alongside the discrete domain of the controller and the
hybrid elements that communicate them.
